WORCS: A Workflow for Open Reproducible Code in Science

### 2020-10-28 paper/reviews_ds.Rmd
respond to reviewer concerning docker

Response: I've never used Docker. Andreas and Aaron - do you think you could clarify why worcs might have benefits over Docker? Should we make this proposed docker container available IN ADDITION to worcs as package?

>>>>

Response: Thank you for this thoughtful suggestion. We explained better why `renv` is more user friendly (because it builds upon the "normal" package workflow of R users). For users familiar with Docker, we have published an image on Docker Hub with all requirements of worcs installed and a Docker specific setup vignette, that is much shorter and given that you know how to use Docker easier.
\Assignment{AP, AB}
\WorkInProgress
\Medium
